Approximation as Differentiation: Notes

### 2025-05-21 main/formal-structures.tex
Move biproduct section after LatGal.

@@

We noted that $\LatGal$ is enriched in $\CMon$, the category of commutative monoids (in fact in $\SemiLat$)
and moreover that the product of lattices is also a coproduct, making $\LatGal$ into a category with
\emph{biproducts}. In fact the presence of biproducts is sufficient for $\CMon$-enrichment; such a category is
called \emph{semi-additive}.

>>>>

We noted that $\LatGal$ is enriched in $\SemiLat$, the category of semilattices, and moreover that the product
of lattices is also a coproduct, making $\LatGal$ into a category with \emph{biproducts}. In fact the presence
of biproducts is sufficient for enrichment in $\CMon$, the category of commutative monoids (including
semilattices); such a category is called \emph{semi-additive}.

@@
